---
title: "Gapminder Analysis"
author: "Maya Craig"
date: "`r Sys.Date()`"
output: html_document:
  toc: yes
  toc_float: yes
  code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this document, I will analyze how life expectancy has changed over time.

# Reading in gapminder data

```{r reading-in-data}
gapminder_df <- read.csv("data/gapminder_data.csv")
```

Lists:

-   item 1
-   item 2

Hyphen list

-   item 1
-   item 2

Make text **bold with asterisks** or *italic with one*

Greek letters $\mu$ or $\Delta$

hyperlinks [hyperlinks](https://pad.carpentries.org/Spring2024-BIOMI6300)

# Calculating summary statistics

```{r calculating-median-pop, echo = FALSE}
med_pop <- median(gapminder_df$pop)
num_obs <- nrow(gapminder_df)
```

Over `r num_obs` observations, the median population was `r round(med_pop/10e6, 3)` million people.

# Plotting life expectancy over the years

```{r line-graph}
library(ggplot2)
ggplot(gapminder_df, aes(x = year, y = lifeExp, group = country, color = continent)) + geom_line() + scale_y_log10()
```

# Plotting population distribution

```{r histogram, message=FALSE, fig.width=10}
ggplot(gapminder_df, aes(x=pop)) + geom_histogram()
```

| Col1 | Col2 | Col3 |
|------|------|------|
|      |      |      |
|      |      |      |
|      |      |      |
